The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-09 src/rev1_reply_comments.tex
Shorten title a little bit, smaller formatting changes, include external doc.

% \setlength{\marginparwidth}{2cm}
\usepackage[ colorinlistoftodos, backgroundcolor=white, prependcaption, textsize=tiny,
    disable, ]{todonotes}

@@

@@

\title{\large Reply to the Editor's and Reviewers' comments on: \\[2ex]
    \LARGE The Effectiveness of Antigen Rapid Diagnostic Tests, Vaccinations, and
    Contact Restrictions for Containing the Covid-19 Pandemic\\[2ex]
    \large Submitted to Scientific Reports (Submission ID
    db917d3c-b56a-4129-8eb1-a62a716aaede)\\[-6ex]
}

@@

\comment{ The title should have a clear, precise scientific meaning and should not
contain a colon. Where possible, the title should be read as one concise sentence. }
\vskip1ex \response{%
    We changed the title from ``The Effectiveness of Strategies to Contain SARS-CoV-2:
    Testing, Vaccinations, and NPIs'' to ``The Effectiveness of Antigen Rapid Diagnostic
    Tests, Vaccinations, and Contact Restrictions for Containing the Covid-19 Pandemic'' }

\section*{Reviewer 1}
\comment{ The authors of the manuscript presented here have used mathematical models to
examine the impact of different measures to contain the SARS-CoV-2 pandemic. Using
epidemiological data from Germany, the contribution of rapid antigen testing is
considered in particular.

@@

          \response{%
              We thank the reviewer for spotting this mistake on our part. We removed
              the reference and only use current information as detailed in the next item. }

@@

          \response{%
              We agree that the references we used have become outdated in the meantime
              (we submitted the paper in  August 2021). Indeed, the numbers we used
              turned out to be too optimistic in light of newer studies.

              We therefore ran additional simulations with updated and more conservative
              assumptions on the sensitivity of rapid tests (Appendix B.12) and found that
              our main results are remarkably robust to this change. The percentage of the
              decrease in spring 2021 attributed to rapid tests decreases by only 4
              percentage points even in the least favourable scenario. We describe our
              approach for calculating the adjusted sensitivities in the next answer. }
    \item I recommend including a declaration of potential conflicts of interest in the
          manuscript.
          \response{We have added such a declaration. There are no competing interests.}

>>>>

% \setlength{\marginparwidth}{2cm}
\usepackage[colorinlistoftodos, backgroundcolor=white, prependcaption, textsize=tiny,
    disable]{todonotes}

@@

\externaldocument{paper}

@@

\title{\large Reply to the Editor's and Reviewers' comments on: \\[2ex]
    \LARGE The Effectiveness of Testing, Vaccinations, and Contact Restrictions for
    Containing the Covid-19 Pandemic\\[2ex]
    \large Submitted to Scientific Reports \\(Submission ID
    db917d3c-b56a-4129-8eb1-a62a716aaede)\\[-6ex]
}

@@

\comment{ The title should have a clear, precise scientific meaning and should not
contain a colon. Where possible, the title should be read as one concise sentence. }
\vskip1ex \response{%
    We changed the title from ``The Effectiveness of Strategies to Contain SARS-CoV-2:
    Testing, Vaccinations, and NPIs'' to ``The Effectiveness of Testing, Vaccinations, and Contact Restrictions for Containing the Covid-19 Pandemic''
}

\section*{Reviewer 1}
\comment{The authors of the manuscript presented here have used mathematical models to
examine the impact of different measures to contain the SARS-CoV-2 pandemic. Using
epidemiological data from Germany, the contribution of rapid antigen testing is
considered in particular.

@@

          \response{%
              We would like to thank the reviewer for spotting this mistake of ours. We
              removed the reference.}

@@

          \response{%
              We agree that the references we used have become outdated in the meantime.
              Note that we submitted the original manuscript in early September 2021;
              the calculations had been done some time before that.

              We therefore ran additional simulations with updated and more conservative
              assumptions on the sensitivity of rapid tests (Appendix~\ref{subsec:robustness_rapid_test_sensitivity}) and found that
              our main results are remarkably robust to this change. The percentage of the
              decrease in spring 2021 attributed to rapid tests decreases by only 4
              percentage points even in the least favourable scenario. We describe our
              approach for calculating the adjusted sensitivities in the next answer. }
    \item I recommend including a declaration of potential conflicts of interest in the
          manuscript.
          \response{We have added such a declaration. There are no competing interests.}
